Uncertainty in Inflation Forecasting Using Bayesian Methods

### 2022-06-15 final_notebook.Rmd
6/15 update1 README brush up

fits = monthly_train %>%
  add_draws(colSums(aperm(model$state.contributions, c(2, 1, 3))))
predictions = monthly_train %$%
  tibble(
    DATE = max(DATE) + months(1:forecast_months),
    m = month(DATE),
    time = max(time) + 1:forecast_months
  ) %>%
  add_draws(predict(model, newdata = monthly_test, horizon = forecast_months)$distribution, value = ".prediction")
predictions_with_last_obs = monthly_train %>% 
  slice(n()) %>% 
  mutate(.draw = list(1:max(predictions$.draw))) %>% 
  unnest(cols = c(.draw)) %>% 
  mutate(.prediction = P) %>% 
  bind_rows(predictions)
```
A first glance at the model's predictive ability below shows its effectiveness at plotting both what has been and what may be, though we take a closer look at the more recent figures going forward.  
```{r}
monthly_train %>%
  ggplot(aes(x = DATE, y = P)) +
  geom_line(aes(y = .value, group = .draw), alpha = 1/20, data = fits %>% sample_draws(100)) +
  geom_line(aes(y = .prediction, group = .draw), alpha = 1/20, data = predictions %>% sample_draws(100)) +
  geom_point()+
  coord_cartesian(ylim = c(-0.02, 0.15))
```

@@

## Posterior Sampling and Visualization
Moving on, the plot below is the fit and forecast starting from 2014. The points are the actual values from the training set, while the blue line is the posterior predictives of the data, having been trained on it. The more interesting portion is the scattering red lines, which are updated prior predictives based on the model fit thus far.
```{r, echo = FALSE}
since_year = 2014
set.seed(123456)
fit_color = "#3573b9"
fit_color_fill = hex(mixcolor(.6, sRGB(1,1,1), hex2RGB(fit_color)))
prediction_color = "#e41a1c"
prediction_color_fill = hex(mixcolor(.6, sRGB(1,1,1), hex2RGB(prediction_color)))

@@

Lastly, while point estimates aren't quite the best use of Bayesian methods, they're included here. These values describe:  
The posterior probability that the variable is positive.  
The conditional expectation of the coefficient, given inclusion.  
The conditional standard deviation of the coefficient, given inclusion  
The posterior probability the variable is included.  
You'll notice that the expected coefficient is positive, which is the opposite of what's expected given prior knowledge of macroeconomics. My best attempt at explaining this would be that the lag used in inflation is simply too short so the model misinterpreted the relationship.
```{r}
summary(model)[6]
```

>>>>

fits = monthly_train %>%
  add_draws(colSums(aperm(model$state.contributions, c(2, 1, 3))))
predictions = monthly_train %$%
  tibble(
    DATE = max(DATE) + months(1:forecast_months),
    m = month(DATE),
    time = max(time) + 1:forecast_months
  ) %>%
  add_draws(predict(model, newdata = monthly_test, horizon = forecast_months)$distribution, value = ".prediction")
predictions_with_last_obs = monthly_train %>% 
  slice(n()) %>% 
  mutate(.draw = list(1:max(predictions$.draw))) %>% 
  unnest(cols = c(.draw)) %>% 
  mutate(.prediction = P) %>% 
  bind_rows(predictions)
```

A first glance at the model's predictive ability below shows its effectiveness at plotting both what has been and what may be, though we take a closer look at the more recent figures going forward.  
```{r}
monthly_train %>%
  ggplot(aes(x = DATE, y = P)) +
  geom_line(aes(y = .value, group = .draw), alpha = 1/20, data = fits %>% sample_draws(100)) +
  geom_line(aes(y = .prediction, group = .draw), alpha = 1/20, data = predictions %>% sample_draws(100)) +
  geom_point()+
  coord_cartesian(ylim = c(-0.02, 0.15))
```

@@

## Posterior Sampling and Visualization
Moving on, the plot below is the fit and forecast starting from 2014. The points are the actual values from the training set, while the blue line is the posterior predictives of the data, having been trained on it. The more interesting portion is the scattering red lines, which are updated prior predictives based on the model fit thus far.

```{r, echo = FALSE}
since_year = 2014
set.seed(123456)
fit_color = "#3573b9"
fit_color_fill = hex(mixcolor(.6, sRGB(1,1,1), hex2RGB(fit_color)))
prediction_color = "#e41a1c"
prediction_color_fill = hex(mixcolor(.6, sRGB(1,1,1), hex2RGB(prediction_color)))

@@

Lastly, while point estimates aren't quite the best use of Bayesian methods, they're included here. These values describe:  
- The posterior probability that the variable is positive.  
- The conditional expectation of the coefficient, given inclusion.  
- The conditional standard deviation of the coefficient, given inclusion  
- The posterior probability the variable is included.  
You'll notice that the expected coefficient is positive, which is the opposite of what's expected given prior knowledge of macroeconomics. My best attempt at explaining this would be that the lag used in inflation is simply too short so the model misinterpreted the relationship.
```{r}
summary(model)[6]
```
